Final Workflow for CLM5 paper

### 2018-10-29 main.tex
Updates from ShareLaTeX

@@

\section{Discussion}
The responses of land surface models to CO$_{2}$ fertilization are the subject of intense investigations, and vast quantities of computing time will be expended on the single release version of each model, under the auspices of the various CMIP model inter-comparison projects and associated activities  (\cite{meehl2014}). In all of these activities, the carbon cycle feedbacks reported by each modeling group will be from a single default instance of the parameter space.  At the time of writing, we do not yet know the climate feedback strength of the default version of CLM5 compared to it's predecessors, but it is clear from these investigations that many model parameters can and will have had a large impact on these outcomes, without necessarily changing the control state to a large extent. As expected, parameters the relate most strongly to the acquisition \emph{frac\_fixers}, \emph{Ncosts} and use \emph{leafcn}, \emph{cn\_flex\_b}, have dominant roles over the fertilization responses to CO$_{2}$ and nitrogen.

\subsection{Limitations of step-change experiments}
Here we propose to investigate the parameter space of the model using step-change experiments. However, such experiments necessarily involve unrealistically rapid changes in environmental boundary condition, and cannot necessarily be considered as analagous to either real-world or transient future scenario conditions. We assessed the response to the ramping historical CO2, to illustrate how parameter responses differed between the rapid and slow responses. The results are in figure SI **

\subsection{Limitations from single sites}
The analysis presented here deliberately does not focus on the relative fit of the model to the data collected at the individual sites. The fit at individual sites of the globally adjusted model cannot be seen as indicative or otherwise of its skill in the absence of specific parameterization using the local vegetation, soil and hydrological characteristics, which is beyond the scope of this paper. Instead, we chose a set of individual sites, rather than global analysis, to allow for the 936 model integrations that comprise our sensitivity tests, and to probe a set of alternative vegetation and climate conditions. This study is incomplete, as are all investigations of the climatic and parameteric space of land surface models.

\subsection{Discussions of parameterization issues}
During the development of CLM5, we conducted extensive testing into the possibility of inverse-calibration of the model using neural network derived emulators, in conjunction with a variety of gridded global data products. We did not use the results of this effort for a variety of reasons, including,  1) the high dimensionality of the space, 2) the degree of non-orthogonal behaviour in the parameter response surfaces,  3) the tendency of the modeled ecosystem to die under past low-CO$_{2}$ conditions when calibrated using present-day CO$_{2}$, 4) the dominance of high productivity areas over the calibration of a particular PFT at the expense of marginal areas, and the resulting pattern that those marginal areas die off in model spin-up, 5) the subjectivity in weighting of the different data products and 6) philosophical issues concerning whether the structural validity of the calibrated model could be independently assessed, given the sparsity of validation datasets. Thus, the parameterization used in the default version of the model is a less objective calibration than is ideal, and a limited set of parameters were tuned 'by hand' to avoid excessively spurious values for some model states.  Given the sensitivity of the fertilization responses in the CLM5, we advocate careful interpretation of the outcome of the model, particularly with regard to the climate feedback strength.

\subsection{How to reduce model uncertainty}
Many model development efforts are motivated under the auspices of 'reducing uncertainty'.  Our efforts to improve the fidelity of the nitrogen cycle in the CLM5 are partly motivated by the need to move the model behaviour closer to several key observable features of the system. Notably, the dynamics of leaf Nitrogen content with respect to environmental scarcity (\cite{zaehle2014}, \cite{brzostek2014}), the dynamics of photosynthetic capacity with respect to environmental conditions (\cite{xu2012}, \cite{ali2016},\cite{rogers2017}), the changes in N fixation rate with vegetation state and the scarcity of N (\cite{vitousek2002}), and to include a means of deploying carbon as a means to acquire additional nitrogen. The latter acts as a proxy for the numerous ways in which plant symbiont systems might adapt to low nutrient conditions, including increases in fine root exudation and allocation, fungal biomass, tissue metabolic rates and turnover/nutrient foraging.  We argue that all of these development generate model emergent behaviour that is closer in essence to reality. However, in doing so, we integrate a suite of physiological processes that lack complete mechanistic and quantititive understanding.

The development of the CLM5 also slightly pre-dated the operational usage of the International Land Model Benchmarking Project (ILAMB) package \cite{collier2016} for assessing model skill across a very broad range of model components.  In principle, integrating more targeted dataset and data products should narrow the range of model parameter sets that are acceptable, as well as accelerate the rejection of model structures that are unrealistic. Ideally, this effort should include synthesis of ecosystem manipulation experiments that provide altered boundary conditions in real life, given the large differences observed here between the sets of parameters affecting present day conditions and those that impact transient responses.

This implies that a critical control in the CLM, and in coupled simulations with the CESM for CMIP are dependant on the representation of Nitrogen fixations and its dynamics.

@@

\subsubsection{Discourse on whether nitrogen fixation is realistic in CLM5}

The 'fraction of fixers' (\emph{frac\_fixers}) is a proxy for the community level composition of Nitrogen fixing plants. Technically, because plant density is not represented in the CLM5, this parameter really represents the fraction of net assimilated carbon ($gpp$ - $R_{auto}$) that can be used for symbiotic N fixation. Ideally, this feature of the model would be prognostic, and the fraction of N fixing plants would response to changes in environmental conditions and the relative competitive abilities of N fixing plants. In general, Nitrogen fixers are known to primarily exist in early successional parts of ecosystems (references**), and therefore representation of their ecological dynamics would likely include a representation of vegetation demographics and succession (\cite{fisher2018vegetation}, \cite{trugman2016climate}). The results included here indicate that the

>>>>

\item This implies that a critical control in the CLM, and in coupled simulations with the CESM for CMIP are dependant on the representation of Nitrogen fixations and its dynamics.

@@

\section{Discussion}
The overall responses of land surface models to CO$_{2}$ fertilization are the subject of intense investigations, and vast quantities of computing time will be expended on the single release version of each model, under the auspices of the various CMIP model inter-comparison projects and associated activities  (\cite{meehl2014}).  In all of these activities, the carbon-cycle feedbacks reported by each modeling group will be from a single default instance of the parameter space.  At the time of writing, we do not yet know the climate feedback strength of the default version of CLM5 compared to it's predecessors, but it is clear from these investigations that many model parameters can and will have had a large impact on these outcomes.  In particular, as expected, parameters that relate most strongly to the acquisition of N, \emph{frac\_fixers}, \emph{Ncosts} and use \emph{leafcn}, \emph{cn\_flex\_b}, have dominant roles over the fertilization responses to CO$_{2}$ and nitrogen.  It has long been understood that uncertainties in the representation of Nitrogen are large(\cite{zaehle2014}) . In the CMIP6 generation of land surface models, it is expected that a much larger number of model submissions will contain active representations of N limitation. We do not yet know how CLM5 compares to others in it's carbon cycle feedback strength, but we propose that understanding the model parameterizations and structural decisions that contribute to the relative fertilization responses is critical to understanding the implications of the range of results obtained.

\subsection{Limitations}
\subsubsection{Limitations of step-change experiments}
Here investigate the parameter space of the model using step-change experiments. However, such experiments necessarily involve unrealistically rapid changes in environmental boundary condition, and cannot necessarily be considered as analagous to either real-world or transient future scenario conditions. We assessed the response to the ramping historical CO2, to illustrate how parameter responses differed between the rapid and slow responses. The results are in figure SI **

\subsubsection{Limitations from single site analyses}
The analysis presented here deliberately does not focus on the relative fit of the model to the data collected at the individual sites. The fit at individual sites of the globally adjusted model cannot be seen as indicative or otherwise of its skill in the absence of specific parameterization using the local vegetation, soil and hydrological characteristics, which is beyond the scope of this paper. Instead, we chose a set of individual sites, rather than global analysis, to allow for the 936 model integrations that comprise our sensitivity tests, and to probe a set of alternative vegetation and climate conditions. This study is incomplete, as are all investigations of the climatic and parameteric space of land surface models.

\subsubsection{Limitations of parameter calibration issues}
During the development of CLM5, we conducted extensive testing into the possibility of inverse-calibration of the model using neural network derived emulators, in conjunction with a variety of gridded global data products. We did not use the results of this effort for a variety of reasons, including,  1) the high dimensionality of the space, 2) the degree of non-orthogonal behaviour in the parameter response surfaces,  3) the tendency of the modeled ecosystem to die under past low-CO$_{2}$ conditions when calibrated using present-day CO$_{2}$, 4) the dominance of high productivity areas over the calibration of a particular PFT at the expense of marginal areas, and the resulting pattern that those marginal areas die off in model spin-up, 5) the subjectivity in weighting of the different data products and 6) philosophical issues concerning whether the structural validity of the calibrated model could be independently assessed, given the sparsity of validation datasets. Thus, the parameterization used in the default version of the model is a less objective calibration than is ideal, and a limited set of parameters were tuned 'by hand' to avoid excessively spurious values for some model states.  Given the sensitivity of the fertilization responses in the CLM5, we advocate careful interpretation of the outcome of the model, particularly with regard to the climate feedback strength.

\subsection{Future Investigations}
\subsubsection{Temperature and water responses}
Here we probe the impacts of parametric uncertainty on the carbon and nitrogen responses of the CLM5. In particular, we probe a targeted parameter set comprising those parameters that determine the impacts of CO$_{2}$ and N fertilization. The full response of the model has considerably more dimensions than these two transient properties. In particular, here we have not considered responses to temperature and moisture changes. The suite of parameters than in principle control temperature responses of the model are somewhat distinct from the parameters considered here, given the large number of processes that are directly or implictly affected by temperature (photosynthesis, respiration, soil decomposition, N mineralization, cryosphere interaction) and should be the subject of further investigations. Properties more closely linked to water availability are associated with the hydrological components of the model as well as the PHS plant hydraulics scheme and will be investigated further by [Dagon et al in prep. and Kennedy et al., in prep.]

\subsubsection{Filtering parameter space with observations}
The development of the CLM5 slightly pre-dated the operational usage of the International Land Model Benchmarking Project (ILAMB) package \cite{collier2016} for assessing model skill across a very broad range of model components.  In principle, integrating more targeted dataset and data products should narrow the range of model parameter sets that are acceptable in comparison with the suite of availble and relevant datasets, as well as accelerate the rejection of model structures that are unrealistic. Ideally, this effort should include synthesis of ecosystem manipulation experiments that provide altered boundary conditions in real life, given the large differences observed here between the sets of parameters affecting present day conditions and those that impact transient responses.

\subsection{The status of the CLM5 representation of plant carbon and nitrogen representation}
Many model development efforts are motivated under the auspices of 'reducing uncertainty'.  Our efforts to improve the fidelity of the nitrogen cycle in the CLM5 are partly motivated by the need to move the model behaviour closer to several key observable features of the system. Notably, the dynamics of leaf Nitrogen content with respect to environmental scarcity (\cite{zaehle2014}, \cite{brzostek2014}), the dynamics of photosynthetic capacity with respect to environmental conditions (\cite{xu2012}, \cite{ali2016},\cite{rogers2017}), the changes in N fixation rate with vegetation state and the scarcity of N (\cite{vitousek2002}), and to include a means of deploying carbon as a means to acquire additional nitrogen. The latter acts as a proxy for the numerous ways in which plant symbiont systems might adapt to low nutrient conditions, including increases in fine root exudation and allocation, fungal biomass, tissue metabolic rates and turnover/nutrient foraging.  We argue that all of these development generate model emergent behaviour that is closer in essence to reality. However, in doing so, we integrate a suite of physiological processes that lack complete mechanistic and quantitative understanding.

@@

\subsubsection{Discourse on whether nitrogen fixation is realistic in CLM5}
The 'fraction of fixers' (\emph{frac\_fixers}) is a proxy for the community level composition of Nitrogen fixing plants. Technically, because plant density is not represented in the CLM5, this parameter really represents the fraction of net assimilated carbon ($gpp$ - $R_{auto}$) that can be used for symbiotic N fixation. Ideally, this feature of the model would be prognostic, and the fraction of N fixing plants would response to changes in environmental conditions and the relative competitive abilities of N fixing plants. In general, Nitrogen fixers are known to primarily exist in early successional parts of ecosystems (references**), and therefore representation of their ecological dynamics would likely include a representation of vegetation demographics and succession (\cite{fisher2018vegetation}, \cite{trugman2016climate}). The results included here indicate that the

### 2018-10-29 workflow2.tex
Updates from ShareLaTeX

\begin{document}
\title{Workflow for CLM5 paper}

@@

\subsection{Make new ensemble param files with high leaf allocation }

Use PFT script

{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/FACE_clm5_ens_oaat.m}}}\\ 
commit b6ba94

Using the basefile. \\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/clm5_params.c171017_highleaf.nc}}} \\
commit c539e89

Output location..\\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/FACE_pftfiles/FACE_CLM_params_may1_highleaf_pi11.nc }}} \\
commit 54f863b

Copy default file into '00'..\\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/FACE_pftfiles/FACE_CLM_params_may1_highleaf_pi00.nc }}} \\
commit 61517c5

\section{Spin-up}
\subsection{Make 1850 spin-up default runs from scratch}
Make single point case from scratch for each site by running this script (based on Charlie's FATES version) three times once for each site (that could be improved on!)..:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/fromscratch_CTSM_make_site_spinup_case_defaults}}}\\
commit 38ced1

The resulting cases are \\
{\color{cyan}{\small{\url{/glade/scratch/rfisher/CLM5_SPR_SPIN_HL_.1x1pt_US-ORN}}}\\
\small{\url{/glade/scratch/rfisher/CLM5_SPR_SPIN_HL_.bci_0.1x0.1_v4.0i}}\\
\small{\url{/glade/scratch/rfisher/CLM5_SPR_SPIN_HL_.1x1pt_Br-cax}}}\\

These are all run out to year 321.

\subsection{Make 1850 spin-up ensembles for each site}

Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_spinup_ensembles}} }\\
commit 2bb89c5

Case names are along the lines of:\\
{\color{cyan}\small{\url{CLM5_bci_0.1x0.1_v4.0i_ens_PI**}}\\
\small{\url{CLM5_1x1pt_Br-cax_ens_PI**}}\\
\small{\url{CLM5_1x1pt_US-ORN_ens_PI*}}}\\

These are all run to y201.

\subsection{Make 1850 spin-up defaults for each site}

Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_spinup_defaults}}}\\
commit 0d2894a

Case names are:\\
{\color{cyan}\small{\url{CLM5_1x1pt_Br-cax_ens_PI00}}}\\
{\color{cyan}\small{\url{CLM5_bci_0.1x0.1_v4.0i_ens_PI00}}}\\
{\color{cyan}\small{\url{CLM5_1x1pt_US-ORN_ens_PI00}}}

\subsection{Analyse output of spinup cases}

Run analysis script on spinup ensemble output (at 1850 CO2). \\
{\color{blue}\small{\url{/glade/p/work/rfisher/git/CLM5_FACE_EXPTS/matlab/CLM5_FACE_senstest_output_mar18.m}}}\\
commit 7043e8b

Output here\\
{\color{magenta}\small{\url{https://github.com/rosiealice/CLM5_FACE_EXPTS/tree/master/matlab/figures\frac_deviation_p1CLM5_1x1pt_Br-cax_ens_PI_y1.png}}}\\
commit 1f9a57c

\section{Transients}

\subsection{Make transient defaults}
Use this script. It employs the 20tr default CO2 ramping, but with an 1850 climate. .\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_defaults}}}\\
commit 36ced2a

Case names are:\\
{\color{cyan}\small{\url{CLM5_1x1pt_Br-cax_ens_transient_PI00}}}\\
{\color{cyan}\small{\url{CLM5_bci_0.1x0.1_v4.0i_ens_transient_PI00}}}\\
{\color{cyan}\small{\url{CLM5_1x1pt_US-ORN_ens_transient_PI00}}}

\subsection{Make transient ensemble}
Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ensembles}}}\\
commit 7b8bca7

Case names are along the lines of:\\
{\color{cyan}\small{\url{CLM5_1x1pt_Br-cax_ens_transient_PI**}}}\\
{\color{cyan}\small{\url{CLM5_bci_0.1x0.1_v4.0i_ens_transient_PI**}}}\\
{\color{cyan}\small{\url{CLM5_1x1pt_US-ORN_ens_transient_PI**}}}

\subsection{Analyse transient ensemble}

\subsection{Elevated CO2}
\subsection{Make elevated CO2 file}
Use this script\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/modify_co2_drivers.m}}}\\
commit 0d4fb93

Which generates\\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/co2_datm_ORNL_ELEV.nc}}}\\
commit 0d4fb93

\subsection{Make elevated CO2 defaults}
Use this script:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ELEV_defaults}}}\\
commit 8e6a3a5

Which uses these user$\_$nl$\_$datm files:\\
{\color{blue}\small{\url{gitpath/co2_files/user_nl_datm_FACE_transient_ELEV_1x1pt_Br-cax}}}\\
{\color{blue}\small{\url{gitpath/co2_files/user_nl_datm_FACE_transient_ELEV_bci_0.1x0.1_v4.0i}}}\\
{\color{blue}\small{\url{gitpath/co2_files/user_nl_datm_FACE_transient_ELEV_1x1pt_US-ORN}}}\\
commit 4cb99a4

And this user$\_$datm.streams.txt.co2tseries.20tr file\\
{\color{blue}\small{\url{gitpath/co2_files/user_datm.streams.txt.co2tseries.20tr}}}\\
commit 41d4aeb

Which references the previous co2 file\\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/co2_datm_ORNL_ELEV.nc}}}\\
commit 0d4fb93

The case names are:\\
{\color{cyan}\small{\url{CLM5_1x1pt_Br-cax_ens_transient_ELEV_PI00}}}\\
{\color{cyan}\small{\url{CLM5_bci_0.1x0.1_v4.0i_ens_transient_ELEV_PI00}}}\\
{\color{cyan}\small{\url{CLM5_1x1pt_US-ORN_ens_transient_ELEV_PI00}}}

\subsection{Make elevated CO2 ensemble}
Use this script:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ELEV_ensembles}}}\\
commit ffe1b6b

The case names are like:\\
{\color{cyan}\small{\url{CLM5_1x1pt_Br-cax_ens_transient_ELEV_PI**}}}\\
{\color{cyan}\small{\url{CLM5_bci_0.1x0.1_v4.0i_ens_transient_ELEV_PI**}}}\\
{\color{cyan}\small{\url{CLM5_1x1pt_US-ORN_ens_transient_ELEV_PI**}}}

\subsection{Analyze elevated CO2 runs}
Use this script:\\
{\color{blue}\small{\url{gitpath/matlab/CLM5_FACE_senstest_output_ELEV_apr18.m}}}\\
commit ec202a0

Creates these figures:
{\color{magenta}\small{\url{gitpath/matlab/figures/frac_deviation_CO2_response_1CLM5_1x1pt_Br-cax_ens_transient_ELEV_PI_y1.png}}}\\
commit 23ce56e

\section{Make runs with LUNA off}

\subsection{Make ensemble spinup runs with LUNA off}
Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_spinup_ensembles}} }\\
commit 88b6508

Case names are along the lines of:\\
{\color{cyan}\small{\url{CLM5_bci_0.1x0.1_v4.0i_ens_PI15*}}\\
\small{\url{CLM5_1x1pt_Br-cax_ens_PI15*}}\\
\small{\url{CLM5_1x1pt_US-ORN_ens_PI15*}}}\\

\subsection{Make default spinup runs with LUNA off}
Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_spinup_defaults_lunaoff}} }\\
commit 88b6508

Case names are along the lines of:\\
{\color{cyan}\small{\url{CLM5_bci_0.1x0.1_v4.0i_ens_PI00_noluna}}\\
\small{\url{CLM5_1x1pt_Br-cax_ens_PII00_noluna}}\\
\small{\url{CLM5_1x1pt_US-ORN_ens_PII00_noluna}}}\\

\subsection{Make transient runs with LUNA off}
Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ensembles}} }\\
commit acdee08

The case names are like:\\
{\color{cyan}\small{\url{CLM5_1x1pt_Br-cax_ens_transient_ELEV_PI15*}}}\\
{\color{cyan}\small{\url{CLM5_bci_0.1x0.1_v4.0i_ens_transient_ELEV_PI15*}}}\\
{\color{cyan}\small{\url{CLM5_1x1pt_US-ORN_ens_transient_ELEV_PI15*}}}

\subsection{Make default transient runs with LUNA off}
Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_defaults_lunaoff}} }\\
commit b26f487

\section{Correct the CO2 fertilization to be all year}
Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/modify_co2_drivers_allyear.m }} }\\
commit 723bbf3

File is here: 
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/mco2_datm_ORNL_ELEV_allyear.nc }} }\\
commit 8604dd9

\subsection{Restart ensemble transients with new CO2 file}
Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ELEV_ensembles}}}\\
commit 9f8c771

\subsection{Restart default transients with new CO2 file}
Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ELEV_defaults}}}\\
commit cc6e00e

\subsection{Restart LUNA defaults transients with new CO2 file}
Use.\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ELEV_defaults_lunaoff}}}\\
commit cc6e00e

\subsection{Analyze new elevated CO2 runs}
Use this script:\\
{\color{blue}\small{\url{gitpath/matlab/CLM5_FACE_senstest_output_ELEV_apr18.m}}}\\
commit  7eab468

Creates these figures:
{\color{magenta}\small{\url{gitpath/matlab/figures/frac_deviation_CO2_response_1CLM5_1x1pt_Br-cax_ens_transient_ELEV_PI_y1.png}}}\\
commit 23ce56e

\section{Add parameters to look at open/closed N cycle}
\subsection{Make namelist files witht this matlab script}
{\color{blue}\small{\url{gitpath/matlab/make_namelist_files.m}}}\\
commit 532c208

Files are in here:
{\color{magenta}\small{\url{gitpath/matlab/namelists/**}}}\\
commit c7633e9

\subsection{Make spinup runs for namelist parameters}
{\color{blue}\small{\url{gitpath//case_scripts/make_site_spinup_ensembles}}}\\
commit faa49a9

\subsection{Analyze spinup results for namelist parameters} 
matlab script modified
{\color{blue}\small{\url{gitpath/matlab/CLM5_FACE_senstest_output_mar18.m
}}}\\
e04d71

\subsection{Make transient runs for namelist parameters}

{\color{blue}\small{\url{gitpath//case_scripts/case_scripts/make_site_transient_ELEV_ensembles}}}\\
commit 96fafee

\subsection{Analyze transient runs for namelist parameters}

{\color{blue}\small{\url{gitpath/matlab/CLM5_FACE_senstest_output_ELEV_mar18.m}}}\\
commit fe1a59

\section{Modify range of FlexCN parameters to completely stop C:N flexibility?}

\subsection{Modified ranges of flex\_cn\_c parameters}

{\color{blue}\small{\url{gitpath/matlab/FACE_clm5_ens_oaat.m 
}}}\\
commit b3f67e9

Parameter files here:
Output location..\\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/FACE_pftfiles/FACE_CLM_params_may1_highleaf_pi13*.nc }}} \\
commit 823385e

\subsection{Set up ensemble runs just for parameter 13}
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_spinup_ensembles}} }\\
b3f67e9

\subsection{Set up transient runs just for parameter 13}
{\color{blue}\small{\url{gitpath//case_scripts/case_scripts/make_site_transient_ELEV_ensembles}}}\\
b3f67e9

\subsection{Analyze new runs}

\section{Add Nitrogen fertilization experiments}
\subsection{Made new +5gCm2 file}

\subsection{Make transient NDEP ensembles}
{\color{blue}\small{\url{gitpath/case_scripts/make_site_transient_NDEP_ensembles}}}\\ 
commit 2e395ef

\subsection{Make transient NDEP defaults}
{\color{blue}\small{\url{gitpath/case_scripts/make_site_transient_NDEP_defaults}}}\\ 
commit 2e395ef

\section{Add additional sites}
added Barrow

\section{add temperature experiments}

\section{add reduced form global sensitivity analysis}

 \section{Figures}
 \subsection{Make Will figure}
 \subsection{Make initial LAI figure}
 \subsection{Make 3D figures of parameter space}

\section{Investigate differences in driving data for single sites vs reanalysis}

>>>>

\begin{document}
\title{Final Workflow for CLM5 paper}

@@

Make ensemble parameter files using

{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/FACE_clm5_ens_oaat.m}}}\\

Using the basefile. \\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/clm5_params.c171017.nc}}} \\

Output location..\\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/FACE_pftfiles/FACE_CLM_params_may1_defpft_pi11.nc }}} \\

Copy default file into '00'..\\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/FACE_pftfiles/FACE_CLM_params_may1_defpft_pi00.nc }}} \\

\section{Spin-up}
\subsection{Make 1850 spin-up default runs from scratch}
Make single point case from scratch for each site by running this script (based on Charlie's FATES version) 'n' times once for each site (that could be improved on!)..:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/fromscratch_CTSM_make_site_spinup_case_defaults}}}\\
